Is high social class always beneficial for survival? Northern Sweden 1801--2013

### 2018-04-16 marginal.Rmd
Small changes

```{r probswabs, fig.cap = "Absolute risk of dying before the age of 65, given survival to age 40, by period and hisclass.", fig.scap = "Absolute risk of dying before 65.", fig.height = 8, out.height = "14cm"}
source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1))
midper <- c(1812.5, 1837.5, 1862.5, 1887.5, 1912.5, 1937.5, 1981, 1991, 2000.5, 2009.5)
refclw <- 1 ## pdw[3, ]
plot(midper, pdw[1, ] / refclw, col = scol[1], type = "b", ylim = c(0.0, 0.55), 
     xlab = "Period", xlim = c(1800, 2015), ##log = "y",
     ylab = "P(die before 65 | alive at 40", axes = FALSE, main = "Women, 40-64", lty = 1, pch = 1)

@@

```{r probsw, fig.cap = "Relative risk of dying before the age of 65, given survival to age 40, by period and hisclass. Reference is worker.", fig.scap = "Relative risk of dying before 65.", fig.height = 8, out.height = "14cm"}
source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1))
midper <- c(1812.5, 1837.5, 1862.5, 1887.5, 1912.5, 1937.5, 1981, 1991, 2000.5, 2009.5)
refclw <- pdw[3, ]
plot(midper, pdw[1, ] / refclw, col = scol[1], type = "b", ylim = c(1/3, 3), 
     xlab = "Period", xlim = c(1800, 2015), log = "y",
     ylab = "Relative risk", axes = FALSE, main = "Women, 40-64", lty = 1, pch = 1)

@@

```{r cumsw2abs, fig.cap = "Remaining years of life before 100 for a 65-year-old, by hisclass and period.", fig.scap = "Differences in expected years of life at 65", fig.height = 8, out.height = "14cm"}
##source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1))
midper <- c(1812.5, 1837.5, 1862.5, 1887.5, 1912.5, 1937.5, 1981, 1991, 2000.5, 2009.5)
mm <- 0 ##resw[3, ]
plot(midper, resw[1, ] - mm, col = scol[1], type = "b", ylim = c(75, 88), xlab = "Period", 
     ylab = "Average death age", axes = FALSE, main = "Women, 65-99")

@@

```{r cumsw2, fig.cap = "Excess years of life (compared to worker) before 100 for a 65-year-old, by hisclass and period.", fig.scap = "Differences in expected years of life at 65", fig.height = 8, out.height = "14cm"}
##source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1))
midper <- c(1812.5, 1837.5, 1862.5, 1887.5, 1912.5, 1937.5, 1981, 1991, 2000.5, 2009.5)
mm <- resw[3, ]
plot(midper, resw[1, ] - mm, col = scol[1], type = "b", ylim = c(-3, 5), xlab = "Period", 
     ylab = "Excess years", axes = FALSE, main = "Women, 65-99")

>>>>

```{r probswabs, fig.cap = "Absolute risk of dying before the age of 65, given survival to age 40, by period and social class.", fig.scap = "Absolute risk of dying before 65.", fig.height = 8, out.height = "14cm"}
source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1))
midper <- c(1812.5, 1837.5, 1862.5, 1887.5, 1912.5, 1937.5, 1981, 1991, 2000.5, 2009.5)
refclw <- 1 ## pdw[3, ]
plot(midper, pdw[1, ] / refclw, col = scol[1], type = "b", ylim = c(0.0, 0.55), 
     xlab = "Period", xlim = c(1800, 2015), ##log = "y",
     ylab = "P(die before 65 | alive at 40", axes = FALSE, main = "Women, 40-64", lty = 1, pch = 1)

@@

```{r probsw, fig.cap = "Relative risk of dying before the age of 65, given survival to age 40, by period and social class. Reference is worker.", fig.scap = "Relative risk of dying before 65.", fig.height = 8, out.height = "14cm"}
source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1))
midper <- c(1812.5, 1837.5, 1862.5, 1887.5, 1912.5, 1937.5, 1981, 1991, 2000.5, 2009.5)
refclw <- pdw[3, ]
plot(midper, pdw[1, ] / refclw, col = scol[1], type = "b", ylim = c(1/3, 3), 
     xlab = "Period", xlim = c(1800, 2015), log = "y",
     ylab = "Relative risk", axes = FALSE, main = "Women, 40-64", lty = 1, pch = 1)

@@

```{r cumsw2abs, fig.cap = "Remaining years of life before 100 for a 65-year-old, by social class and period.", fig.scap = "Differences in expected years of life at 65", fig.height = 8, out.height = "14cm"}
##source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1))
midper <- c(1812.5, 1837.5, 1862.5, 1887.5, 1912.5, 1937.5, 1981, 1991, 2000.5, 2009.5)
mm <- 0 ##resw[3, ]
plot(midper, resw[1, ] - mm, col = scol[1], type = "b", ylim = c(75, 88), xlab = "Period", 
     ylab = "Average death age", axes = FALSE, main = "Women, 65-99")

@@

```{r cumsw2, fig.cap = "Excess years of life (compared to worker) before 100 for a 65-year-old, by social class and period.", fig.scap = "Differences in expected years of life at 65", fig.height = 8, out.height = "14cm"}
##source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1))
midper <- c(1812.5, 1837.5, 1862.5, 1887.5, 1912.5, 1937.5, 1981, 1991, 2000.5, 2009.5)
mm <- resw[3, ]
plot(midper, resw[1, ] - mm, col = scol[1], type = "b", ylim = c(-3, 5), xlab = "Period", 
     ylab = "Excess years", axes = FALSE, main = "Women, 65-99")
